Dynamic Transition Analysis with TIMES

### 2019-01-24 doc/2019-02-presentation/assums.tex
Update assums.tex

>>>>

\begin{frame}
\frametitle{Contribution to peak factor (C2P factor}
This is a TIMES parameter that defines what fraction of a energy source's capacity is guaranteed to be available during peak demand.
\begin{tabular}{|c|c|}
\textbf{Energy source} &
\textbf{C2P factor} \\
\hline 
Fossil fuels & 1 \\
Nuclear power & 1 \\
Solar power & 0.42 \\
Wind & 0.20 \\
\end{tabular}

This factor is reduced for solar and wind with increasing penetration.
\end{frame}
